\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{geometry}
\geometry{left=0.5in, top=0.5in, right=0.5in, bottom=0.5in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\begin{document}

% --- HEADER ---
\begin{center}
    \textbf{\Huge \scshape Udit Jain} \\ \vspace{4pt}
    \textbf{Computer Vision Engineer | AI Specialist} \\ \vspace{4pt}
    \small \href{mailto:uditjainiitd@gmail.com}{uditjainiitd@gmail.com} $|$
    \href{https://www.linkedin.com/in/uditjainiitd/}{linkedin.com/in/uditjainiitd} $|$
    \href{https://github.com/udit01}{github.com/udit01} $|$
    \href{https://udit01.github.io}{udit01.github.io}
\end{center}


% --- EDUCATION ---
\section{Education}
  \resumeSubheading
    {Indian Institute of Technology, Delhi (IIT Delhi)}{New Delhi, India}
    {Bachelor of Technology in Computer Science and Engineering; CGPA: 9.10/10.0}{2016 -- 2020}
    \resumeItem{Specialization: Artificial Intelligence, Computer Vision, Systems Programming}


% --- EXPERIENCE ---
\section{Experience}
  \begin{itemize}[leftmargin=0.15in, label={}]
  
    \resumeSubheading
      {Samsung Research}{Seoul, South Korea}
      {Computer Vision Engineer}{2020 -- Present}
      \resumeItem{Lead engineer for vision systems in the \textbf{Samsung Bespoke AI Refrigerator}, enabling real-time food recognition and inventory tracking.}
      \resumeItem{Designed and deployed end-to-end deep learning pipelines (detection, segmentation, tracking) on resource-constrained edge devices.}
      \resumeItem{Optimized inference latency using \textbf{TensorFlow Lite}, quantization, and knowledge distillation for embedded NPU targets.}
      \resumeItem{Awarded \textbf{Data Science Level 2 Certification} and \textbf{Professional AI Certification} by Samsung Electronics.}
      \resumeItem{Collaborated with global teams to integrate AI features into consumer appliances, showcased at \textbf{CES 2024}.}

    \resumeSubheading
      {Kyutech Institute of Technology}{Kitakyushu, Japan}
      {Robotics Research Intern}{Summer 2019}
      \resumeItem{Developed an \textbf{Elderly Clothing Assistance} system using the BAXTER robot and ROS (Robot Operating System).}
      \resumeItem{Implemented 3D sensing and path planning algorithms for human-robot interaction.}
      \resumeItem{Project showcased at \textbf{RoboMech} and \textbf{iREX 2019}, receiving coverage on Japanese national television.}

    \resumeSubheading
      {Harvard University}{Cambridge, USA}
      {Research Intern}{Summer 2018}
      \resumeItem{Contributed to advanced research projects focusing on technology development and cross-cultural collaboration.}
      \resumeItem{Gained global perspective on large-scale software engineering and academic research practices.}

  \end{itemize}


% --- PROJECTS & PUBLICATIONS ---
\section{Key Projects \& Publications}
  \begin{itemize}[leftmargin=0.15in, label={}]

    \resumeProjectHeading
      {\textbf{APEX: Adaptive Ext4 File System} $|$ \emph{Reinforcement Learning, Systems}}{2019}
      \resumeItem{Co-authored paper published in \textbf{IEEE Cloud Computing 2019}.}
      \resumeItem{Designed a novel file system for edge devices that improves data recoverability using reinforcement learning.}

    \resumeProjectHeading
      {\textbf{Samsung Health Research Stack} $|$ \emph{Data Engineering, UX}}{2023}
      \resumeItem{Contributed to the development of a UX Design Award-winning platform for medical researchers.}
      \resumeItem{Enabled large-scale collection and visualization of health data.}

    \resumeProjectHeading
      {\textbf{Transformative Effects of IoT \& Blockchain} $|$ \emph{Cloud Computing}}{2019}
      \resumeItem{Published comprehensive analysis in Distibuted, Parallel, and Cluster Computing (cs.DC).}

  \end{itemize}


% --- SKILLS ---
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, Java, Kotlin, SQL, Shell} \\
     \textbf{AI \& CV}{: PyTorch, TensorFlow, Keras, OpenCV, Object Detection, Segmentation, TFLite} \\
     \textbf{Data \& Cloud}{: AWS (S3, EMR), Spark, Hadoop, Docker, Git, CI/CD} \\
     \textbf{Robotics}{: ROS, Point Cloud Processing, Embedded Systems}
    }}
 \end{itemize}

\end{document}
