\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{geometry}
\geometry{left=0.5in, top=0.5in, right=0.5in, bottom=0.5in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\begin{document}

% --- HEADER ---
\begin{center}
    \textbf{\Huge \scshape Udit Jain} \\ \vspace{4pt}
    \textbf{AI Engineer | Data Scientist} \\ \vspace{4pt}
    \small \href{mailto:uditjainiitd@gmail.com}{uditjainiitd@gmail.com} $|$
    \href{https://www.linkedin.com/in/uditjainiitd/}{linkedin.com/in/uditjainiitd} $|$
    \href{https://github.com/udit01}{github.com/udit01} $|$
    \href{https://udit01.github.io}{udit01.github.io}
\end{center}


% --- EDUCATION ---
\section{Education}
  \resumeSubheading
    {Indian Institute of Technology, Delhi (IIT Delhi)}{New Delhi, India}
    {Bachelor of Technology in Computer Science and Engineering; CGPA: 9.10/10.0}{2016 -- 2020}
    \resumeItem{Relevant Coursework: Algorithms, Probability \& Statistics, Linear Algebra, Machine Learning}


% --- EXPERIENCE ---
\section{Experience}
  \begin{itemize}[leftmargin=0.15in, label={}]
  
    \resumeSubheading
      {Samsung Research}{Seoul, South Korea}
      {Research Engineer}{2020 -- Present}
      \resumeItem{Conducted large-scale data analysis on sleep patterns using anonymized data from millions of Samsung Health users.}
      \resumeItem{Implemented statistical models (time series forecasting, significance testing) to identify global behavioral shifts during the COVID-19 pandemic; findings featured in global media.}
      \resumeItem{Built and optimized data processing pipelines using \textbf{Spark} and \textbf{SQL} to handle terabytes of health data.}
      \resumeItem{Developed \textbf{Samsung Health Research Stack}, a platform enabling medical researchers to collect and analyze granular health metrics.}
      \resumeItem{Awarded \textbf{Data Science Level 2 Certification} (Advanced Statistical Analysis) by Samsung Electronics.}

    \resumeSubheading
      {Harvard University & Kyutech (Japan)}{International}
      {Research Intern}{2018 -- 2019}
      \resumeItem{Gained global research experience working on complex systems and algorithmic challenges.}
      \resumeItem{Applied mathematical modeling to optimize robotic path planning and control systems.}

  \end{itemize}


% --- RESEARCH & PROBLEM SOLVING ---
\section{Mathematical Research \& Projects}
  \begin{itemize}[leftmargin=0.15in, label={}]

    \resumeProjectHeading
      {\textbf{Two-Color Disjunctive Rado Number} $|$ \emph{Combinatorial Number Theory}}{Under Review}
      \resumeItem{Researched Ramsey Theory applications to systems of linear equations.}
      \resumeItem{Developed novel algorithms to solve complex coloring problems, optimizing search space reduction.}

    \resumeProjectHeading
      {\textbf{APEX: Adaptive Ext4 File System} $|$ \emph{Reinforcement Learning, Systems}}{2019}
      \resumeItem{Designed an adaptive file system using Reinforcement Learning for optimized data recoverability.}
      \resumeItem{Formulated the recovery problem as an MDP and trained agents to minimize data loss probability.}

    \resumeProjectHeading
      {\textbf{Kaggle \& Competitive Programming}}{Ongoing}
      \resumeItem{Active participant in predictive modeling competitions; leveraging ensemble methods and feature engineering.}
      \resumeItem{Strong proficiency in Data Structures and Algorithms (C++/Python).}

  \end{itemize}


% --- SKILLS ---
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: C++, Python (NumPy, Pandas, Scipy), SQL, Java} \\
     \textbf{Quantitative Analysis}{: Time Series Analysis, Statistical Modeling, Hypothesis Testing, A/B Testing} \\
     \textbf{Data Engineering}{: Spark, Hadoop, AWS (Athena, Glue), BigQuery} \\
     \textbf{Machine Learning}{: Deep Learning (PyTorch/TF), Regression, Clustering, Dimensionality Reduction}
    }}
 \end{itemize}

\end{document}
